Stability and Chaos in Multi-agent Reinforcement Learning

### 2020-10-09 aamas2021-formatting-instructions/aamas21-formatting-instructions/sample.tex
minor mods

\paragraph{Evolutionary Game Dynamics}
The theory of evolutionary game dynamics \cite{Morgenstern44}
considers the case in which agents must repeatedly interact with one
another. The outcome of this interaction depends on a payoff matrix;
'strong' strategies which maximise the reward are promoted whilst
'weaker' strategies diminish. The \textit{replicator dynamic} models
this behaviour, and allows one to determine whether, after a number of
iterations, the game is likely to converge to some fixed equilibrium
and, if so, the probabilities with which strategies are played in this
equilibrium. \cite{ShohamMultiagentFoundations} provides an excellent
introduction to the replicator dynamic for the interested reader.

Analyses have been performed from the point of view of the replicator
dynamic towards the various types of behaviours that can emerge from
iterated games. Such games are considered imperfect, in that agents
make decisions by attempting to anticipate their opponents' behaviour
based on experience \cite{Galla2011}. \cite{Imhof2005} presents the
observation that, in the game of Prisoner's Dilemma, cyclic behaviour
emerges in which the optimal strategy cycles across defection,
cooperation and tit-for-tat despite defection being the
NE. \cite{Galla2011} builds on this notion by showing that, in fact,
such behaviour is highly dependent on the presence of memory loss in
the system. In the absence of memory loss, the learning converges to
the NE as expected. However, as this parameter is increased, the
stability of the NE is removed and other stable points are created.

Taking this notion even further, \cite{Galla2013} describes an
investigation of two-person iterated games in which the players learn
using \textit{Experience Weighted Attraction} (EWA), a form of
reinforcement learning whose analysis typically falls under the
purview of experimental economics \cite{Camerer2009}. Through
numerical simulations, the authors were able to show that, once again,
the emergence of chaos and cycles (see \cite{Strogatz2000} for details
on chaotic and periodic motion), is dependent on the choice of
parameters. A rigorous theoretical analysis, which applies the
techniques presented in \cite{Opper1992}, of the replicator dynamic
corresponding to EWA presented a method for characterising the regions
in parameter space in which a game is likely to converge, exhibit
chaos or limit cycles. More recently, the authors presented an
extended study in \cite{Sanders2018}, in which this analysis was
extended towards a generic $p$-player game, which showed that chaotic
dynamics are more likely to be observed as the number of players
\textit{p} increases.

@@

\paragraph{Dynamics of RL}
In \cite{Tuyls2006AnGames}, the authors are able to derive a relation
between Q-Learning (see \cite{Barber2012}) and the replicator
dynamic. In doing so, the authors present an evolutionary model which
accurately predicts the dynamics of Q-Learning. This sprung forward a
vast array of literature which perform similar derivations for various
reinforcement learning algorithms. \cite{Bloembergen2015} presents an
excellent review of these. In particular it should be noted that many
of these studies focus on normal form games, in which the payoff
matrix does not change (i.e. the environment is static). Recent work,
such as \cite{Hennes2008}, extends this work towards multi-state
games, though this is restricted to 2 state games. Similarly,
\cite{Galstyan2013}, extends the work in \cite{Tuyls2006AnGames}
towards games with continuous action spaces. Most recently,
\cite{Hu2019} considers Q-learning in the mean-field limit, in which
the strategies of populations of agents are considered.

>>>>

\paragraph{Evolutionary Game Dynamics}
The theory of evolutionary game dynamics \cite{Morgenstern44}
considers game-like settings in which agents must repeatedly interact
with one another. The outcome of this interaction depends on a payoff
matrix; 'strong' strategies which maximise the reward are promoted,
whilst 'weaker' strategies diminish. The \textit{replicator dynamic}
models this behaviour, and allows one to determine whether, after a
number of iterations, the game is likely to converge to some fixed
equilibrium and, if so, the probabilities with which strategies are
played in this equilibrium (see \cite{ShohamMultiagentFoundations}
for an excellent introduction to the replicator dynamics).

Analyses have been performed from the point of view of the replicator
dynamic towards the various types of behaviours that can emerge from
iterated games. Such games are considered imperfect, in that agents
make decisions by attempting to anticipate their opponents' behaviour
based on experience \cite{Galla2011}. \cite{Imhof2005} presents the
observation that, in the game of Prisoner's Dilemma, cyclic behaviour
emerges in which the optimal strategy cycles across defection,
cooperation and tit-for-tat despite defection being the
NE. \cite{Galla2011} builds on this observation by showing that, in fact,
such behaviour is highly dependent on the presence of memory loss in
the system. In the absence of memory loss, the learning converges to
the NE as expected. \fb{I think we can remove this last couple of lines if need be: However, as this parameter is increased, the
stability of the NE is removed and other stable points are created.}

Taking this notion \fb{which one?} even further, \cite{Galla2013}
describes an analysis of two-person iterated games in which the
players learn using \textit{experience weighted attraction} (EWA), a
form of reinforcement learning typically applied in experimental
economics \cite{Camerer2009}. Through numerical simulations, the
authors were able to show that the emergence of chaos and cycles is
dependent on the choice of parameters (see \cite{Strogatz2000} for
details on chaotic and periodic motion). A rigorous theoretical
analysis of the replicator dynamic corresponding to EWA, which applies
the techniques in \cite{Opper1992}, presented a method for
characterising the regions in parameter space in which a game is
likely to converge, exhibit chaos or limit cycles. More recently, the
same authors presented an extended study in \cite{Sanders2018}, in which
this analysis was extended towards a generic $p$-player game, which
showed that chaotic dynamics are more likely to be observed as the
number of players \textit{p} increases.

@@

\paragraph{Dynamics of RL}
In \cite{Tuyls2006AnGames}, the authors are able to derive a relation
between Q-Learning (see \cite{Barber2012}) and the replicator
dynamic. In doing so, the authors present an evolutionary model which
accurately predicts the dynamics of Q-Learning. This sprung forward a
vast array of literature which perform similar derivations for various
reinforcement learning algorithms (see \cite{Bloembergen2015} for an
excellent literature review). In particular it should be noted that
many of these studies focus on normal form games, in which the payoff
matrix does not change (i.e., the environment is static). Recent work,
such as \cite{Hennes2008}, extends this framework towards multi-state
games.
%though this is restricted to 2 state games.
Similarly, \cite{Galstyan2013}, extends the work in
\cite{Tuyls2006AnGames} towards games with continuous action
spaces. Most recently, \cite{Hu2019} considers Q-learning in the
mean-field limit, in which the strategies of populations of agents are
considered, rather than individuals.
